% Professional Reflection
\section*{Professional Reflection}
\subsection*{Role Overview}
Your report will not be accepted if this section is missing and your marker will ask you to resubmit a new report with the included section. This section contains three mandatory subsections and should be at least one page but no longer than two pages. The professional reflection should be at least 150 words, appear by itself on a separate page(s) and is the only section of the report that may be written in the first person.

\subsection*{Role Overview}
\begin{itemize}
  \item Describe the main technical tasks that were undertaken as a part of your role with the
        company.
  \item Identify if you worked with the development team, testing team etc. and give general details
        about team collaboration and support.
\end{itemize}

\subsection*{Technical Skills \& Industry Knowledge}
\begin{itemize}
  \item Discuss the technical tools used during the work term i.e. programming languages, development platform or framework, e.g. Python, React, Ruby on Rails, and reflect on how the exposure to these tools impacts your technical skills. Include information on any course you have taken during your studies to date that gave you exposure to any of the languages or tools you highlight.
  \item Discuss how the work term increased your industry knowledge and provided additional awareness of the associated tasks for the specific role.
\end{itemize}

\subsection*{Career Goal Impact}
\begin{itemize}
  \item Discuss some of the personal (nontechnical) aspects of your work term. For example, you could discuss how working in the particular role may impact your career objectives; if the experience on the work term will impact the remainder of your academic studies (courses to take etc.) and whether the size and dynamics of the team and work environment informed your current or future expectations about the kind of companies you would target in the future.
\end{itemize}
